---
title: "report"
output: html_document
---

# add code for each section
```{r}
library(readr)
library(dplyr)
library(here)
```

```{r}
here::i_am(
  "report.Rmd"
)

data <- readRDS(here::here("data/clean_data.rds"))
```

## Multivariable Regression Analysis

We conducted multivariable logistic regression analyses to examine the association between demographic and clinical factors and three severe COVID-19 outcomes: ICU admission, intubation, and death. Each model included age, sex, and comorbidities such as pneumonia, diabetes, COPD, asthma, immunosuppression, hypertension, cardiovascular disease, obesity, renal disease, and tobacco use.

The results are presented as odds ratios with 95% confidence intervals. An odds ratio greater than 1 indicates increased odds of the outcome, while an odds ratio less than 1 indicates decreased odds.

The table below summarizes the regression results for all three outcomes, allowing comparison of the relative importance of different predictors across ICU admission, intubation, and mortality.

```{r, regression analysis code}

```

